---
title: "Weight of Fish"
author: "Precious Calderon"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
Fish <- read.csv(file ="Fish.csv")
```




# Predicting Fish Weight


## Perch
```{r}
Perch <- filter(Fish, Species == "Perch")
Perch <- select(Perch, -Species) 
```



### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best regressor model is whichever is the highest up the chart. In this case, it's going to be height and weight. 

### Best Two regressor model

The best two regressor model is whichever is closest to the subset size of 2. In this case, it is the same as the best regressor model which is are height and weight. 


## Pike

### Best Models

### Best Two regressor model

## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements