---
title: "Weight of Fish"
author: "Precious Calderon"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
Fish <- read.csv(file ="Fish.csv")
```




# Predicting Fish Weight


## Perch
```{r}
Perch <- filter(Fish, Species == "Perch")
Perch <- select(Perch, -Species) 
```



### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best regressor model is whichever is the highest up the chart. In this case, it's going to be height and weight, with an adjusted R value of 0.9400. 

### Best Two regressor model

The best two regressor model is whichever is closest to the subset size of 2. In this case, it is the same as the best regressor model which are height and weight. 


## Pike

```{r}
Pike <- filter(Fish, Species == "Pike")
Pike <- select(Pike, -Species) 
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

It seems, based on the plot above, that there are multiple models that would predict the weight of pikes. According to the plot above, Length1 and Length 2 are the best models, along with Length3, Height and Width. 

### Best Two regressor model

The best two regressor model, on the other hand, are Length1 and Length3, as they are the closest to the subset size of 2. 

## Roach

```{r}
Roach <- filter(Fish, Species == "Roach")
Roach <- select(Roach, -Species) 
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

Based on the plot above, the best models that predict the weight of a roach are Length3 and Weight which has the highest adjusted R value among the models. 

### Best Two regressor model

The best two regresser model in predicting the weight of a roach are also Length3 and Weight. 

## Final Summary Statements